The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-06-10 albatros_paper.tex
HCC added figure of command module for single station

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
    \caption{Single autonomous station pathfinder installed at the
      hydro shack site.  The system is powered by a bank of solar
      panels that are visible in the background.  \attention{
        Add command module and electronics glamor shots.}}
    \label{Fig:autonomous}
  \end{center}
\end{figure}

% single element block diagram goes here
\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{Figures/albatros_single_schematic/albatros_single_schematic.pdf}
    \caption{Single-antenna autonomous station block diagram. 
      A dual-polarization LWA
      antenna, equipped with an active balun (described above in \ref{section:FEE}), connects via 50m
      coaxial cables to the back-end readout electronics, 
      housed in a Faraday cage denoted by the dashed box. 
      The antenna signals are passed
      to a second-stage electronics chain consisting of filters and further amplfication.  The signals are
      digitized at 250~Msamp/s by a SNAP board, which includes an on-board FPGA that computes spectra from both antennas.  
      A Raspberry Pi controls the SNAP board, receives the spectrum of interest from the SNAP, and saves it as baseband data.}
    \label{Fig:Signal Chain}
  \end{center}
\end{figure}
\attention{Nivek?} \\

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Figures/autonomous.jpg} 
        \caption{} \label{Fig:autonomous_antenna}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.48\textwidth}
      \centering
        \includegraphics[width=\linewidth]{Figures/container.jpg}
        \caption{} \label{Fig:autonomous_electronics}
    \end{subfigure}
    \caption{{\bf (a)} Single autonomous station pathfinder installed
      at the hydro shack site.  The system is powered by a bank of
      solar panels that are visible in the background. {\bf (b)} A
      weather-proof container, which sits near the solar panels,
      houses the batteries, solar charge controller, and readout
      electronics.}\label{Fig:autonomous}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{Figures/albatros_single_schematic/albatros_single_schematic.pdf}
    \caption{Single-antenna autonomous station block diagram. 
      A dual-polarization LWA
      antenna, equipped with an active balun (described above in \ref{section:FEE}), connects via 50m
      coaxial cables to the back-end readout electronics, 
      housed in a Faraday cage denoted by the dashed box. 
      The antenna signals are passed
      to a second-stage electronics chain consisting of filters and further amplfication.  The signals are
      digitized at 250~Msamp/s by a SNAP board, which includes an on-board FPGA that computes spectra from both antennas.  
      A Raspberry Pi controls the SNAP board, receives the spectrum of interest from the SNAP, and saves it as baseband data.}
    \label{Fig:Signal Chain}
  \end{center}
\end{figure}
\attention{Nivek?} \\
